---
title: "Untitled"
author: "pdf"
date: "2024-05-29"
output: html_document
---

1.Data set: The thicknesses of three different types of table tennis rubbers were measured. I have created this data as a data frame in R

```{r}
rubber_data <- data.frame(
  RubberType = factor(rep(c("Smooth", "PipsOut", "AntiSpin"), each = 6)),
  Thickness = c(2.3, 2.2, 2.15, 2.1, 1.9, 2.0, 1.5, 1.6, 1.1, 1.8, 1.7, 1.4, 2.3, 2.00, 1.5, 2.1, 1.8, 1.5)
)


```



2. Normality Test
We check whether the data distributions of the groups are normal using the Shapiro-Wilk test

```{r}
shapiro_results <- lapply(split(rubber_data$Thickness, rubber_data$RubberType), shapiro.test)
shapiro_results


```
3. Test of Homogeneity of Variances (Levene's Test)
Levene's test checks whether the variances of the groups are homogeneous

```{r}
if (!require(car)) {
  install.packages("car", dependencies = TRUE)
  library(car)
}

levene_test <- leveneTest(Thickness ~ RubberType, data = rubber_data)
levene_test

```

4. ANOVA Analysis
A one-way ANOVA test is applied to analyze the differences between groups

```{r}
# ANOVA
anova_model <- aov(Thickness ~ RubberType, data = rubber_data)
summary(anova_model)


```

5.Post Hoc Tests
```{r}
# Tukey HSD
tukey_test <- TukeyHSD(anova_model)
tukey_test

```

